%-------------------------
% Resume in LaTeX
% Author: Adapted by Assistant
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.4in}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Custom commands for section headers and content
\titleformat{\section}{
  \scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-1pt}]

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeCompactProjectHeading}[2]{
  \vspace{-1pt}\item
    \textbf{#1} \textit{\scriptsize\textbf{$|$ #2}} \vspace{-4pt}
}


\newcommand{\resumeItem}[1]{\item\small{{#1}\vspace{-2pt}}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}}


% Reduce spacing between items in itemize environments
\setlist[itemize]{itemsep=4pt, topsep=6pt, parsep=1pt, partopsep=-1pt}

% Tighten tabular rows (used in \resumeSubheading)
\renewcommand{\arraystretch}{0.95}

%-------------------------------------------
% RESUME STARTS HERE
%-------------------------------------------

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Matthew Arenivas} \\
    \small US Citizen $|$ 623-556-6656 $|$ \href{mailto:arenivasmatheu@gmail.com}{\underline{arenivasmatheu@gmail.com}} $|$
    \href{https://linkedin.com/in/matthew-arenivas-505b47255/}{\underline{LinkedIn}} $|$ \href{https://arenivas.vercel.app/}{\underline{Portfolio Website}}
    \end{center} 

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Arizona State University}{August 2022 -- May 2026}
      {Bachelor of Science in Computer Science}{Tempe, AZ}
    \resumeSubheading
      {Coursework and Certifications}{} 
      {Data Structures and Algorithms, Database Management, Object Oriented Programming, UI/UX Design}{}
  \resumeSubHeadingListEnd

  %-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\resumeSubHeadingListStart
    \resumeItem{\textbf{Languages \& Tools:} Java, Rust, C/C\#/C++, Python, JavaScript, TypeScript, SQL, Bash, Git, Figma, Jira}
    \resumeItem{\textbf{Frameworks \& Libraries:} React.js, Vue.js, Node.js, Next.js, Tailwind CSS, Flask}
    \resumeItem{\textbf{Databases \& DevOps:} AWS, ElasticSearch, PostgreSQL, MySQL, Docker, Kubernetes}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

\resumeSubheading
  {Software Engineer}{August 2025 -- Present}
  {Knight-Swift Transportation \scriptsize\textbf{$|$ JavaScript, VueJS, C\#, .NET, ElasticSearch, Git, Agile Methodologies}}{Phoenix, AZ}
\resumeItemListStart
  \resumeItem{Contribute to cross-functional application teams with a primary focus on user-facing frontend solutions.}
  \resumeItem{Collaborate with fellow software engineers to streamline API consumption, ensuring smooth data flow between distributed systems.}
  \resumeItem{Leverage Agile practices to deliver iterative updates, improve sprint velocity, and reduce feature delivery time.}
\resumeItemListEnd

\resumeSubheading
  {Software Engineer Intern}{August 2025 -- Present}
  {General Dynamics (Capstone Project) \scriptsize\textbf{$|$ Rust, Git, Agile Methodologies}}{Tempe, AZ}
\resumeItemListStart
  \resumeItem{Developed a high-performance \textbf{Rust}-based web server and packet sniffer, enabling efficient low-level network monitoring and data analysis.}
  \resumeItem{Implemented safe concurrency patterns in \textbf{Rust} to handle multiple packet streams without data loss or race conditions.}
  \resumeItem{Optimized memory usage and throughput for network data capture, improving reliability under heavy traffic loads.}
    \resumeItem{Collaborated on version control workflows with \textbf{Git} and \textbf{Jira}, ensuring code quality, traceability, and team-wide consistency.}
\resumeItemListEnd

\resumeSubheading
  {Software Engineer Intern}{June 2025 -- August 2025}
  {Knight-Swift Transportation \scriptsize\textbf{$|$ JavaScript, VueJS, C\#, .NET, ElasticSearch, DBeaver}}{Phoenix, AZ}
\resumeItemListStart
  \resumeItem{Engineered an interactive route visualization tool with \textbf{VueJS}, integrating geospatial data overlays to enhance fleet operations.}
  \resumeItem{Designed and executed regression and functional test suites, improving system reliability and ensuring production readiness across enterprise platforms.}
\resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

  \resumeCompactProjectHeading
    {FireFlyt}{Arduino, C++, JavaScript, Python, Git, Lean Principles}
  \resumeItemListStart
    \resumeItem{Built an autonomous drone system to detect, localize, and map active wildfires using onboard sensors and real-time data processing.}
    \resumeItem{Led a team of software engineers to design and deploy a \textbf{Next.js} web dashboard providing real-time visualization of drone location, wildfire boundaries, and sensor readings.}
    \resumeItem{Integrated frontend and backend systems via \textbf{RESTful APIs} to enable seamless real-time updates and user interaction.}
  \resumeItemListEnd

 \resumeCompactProjectHeading
  {Interplanetary Initiative Lab \scriptsize\textbf{$|$ C++, JavaScript, CesiumJS, Git, Agile Methodologies}}
\resumeItemListStart
  \resumeItem{Developed an interactive \textbf{CesiumJS}-based 3D visualization platform to model atmospheric flight trajectories with dynamic altitude-driven rendering.}
  \resumeItem{Implemented a robust \textbf{C++} flash data retrieval system for embedded devices, featuring serial communication, progress feedback, and optimized memory utilization.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}

